### 2014-05-08 intro.tex
Edit thru chapter 3

By having an explicit model of the user interface at both sides of the
connection, the Mosh client is able to predict the application's
behavior in response to user keystrokes and (if confident in its
predictions) can speculatively display the result---generally an
echoed keystroke or cursor motion---before it has been confirmed by
the server. In practice, in a trace-based evaluation using 40 hours of
real-world usage, Mosh was able to show immediately the results of
\textbf{70\%} of user keystrokes.

@@

\textbf{Remy} (Chapter~\ref{chap:remy}) expands Sprout to the
classical problem of \emph{multi-agent} congestion control, where many
independent users may contend for the same limited network resource. Remy
is a protocol-design tool that takes, as input, a set of assumptions
about the uncertain network and workload, and an objective to pursue
on behalf of the application. Remy's computer-generated algorithms can
achieve higher performance and greater fairness than some
sophisticated human-designed schemes, including ones that put
intelligence inside the network.

>>>>

By having an explicit model of the user interface at both sides of the
connection, the Mosh client can predict the application's behavior in
response to user keystrokes and (if confident in its predictions)
speculatively display the result---generally an echoed keystroke or
cursor motion---before it has been confirmed by the server. In a
trace-based evaluation over 40 hours of real-world usage, Mosh was
able to successfully predict and immediately display the result of
\textbf{70\%} of user keystrokes.

@@

\textbf{Remy} (Chapter~\ref{chap:remy}) generalizes Sprout to address
the classical problem of \emph{multi-agent} congestion control, where
independent users contend for the same limited network resource. Remy
is a protocol-design tool that takes, as input, a set of assumptions
about the uncertain network and workload, and an objective to pursue
on behalf of the application. Remy's computer-generated algorithms can
achieve higher performance and greater fairness than some
sophisticated human-designed schemes, including ones that put
intelligence inside the network.

On a simulated 15~Mbps fixed-rate link with eight senders contending and
an RTT of 150~ms, a computer-generated congestion-control algorithm
achieved the following improvements in median throughput and
reductions in median queueing delay over these existing protocols:

\begin{center}

\begin{tabular}{|l|c|c|}
\hline
Protocol & Median speedup & Median delay reduction \\
\hline
\hline
Compound & $2.1\times$ & $2.7\times$ \\
NewReno & $2.6\times$ & $2.2\times$ \\
Cubic & $1.7\times$ & $3.4\times$ \\
Vegas & $3.1\times$ & $1.2\times$ \\
\hline
Cubic/sfqCoDel & $1.4\times$ & $7.8\times$ \\
XCP & $1.4\times$ & $4.3\times$ \\
\hline
\end{tabular}

{\footnotesize Adapted from \S\ref{sec:remyresults}.}

### 2014-05-08 remy_design.tex
Edit thru chapter 3

Instead, we approximate the solution by greatly abridging the sender's
state. A RemyCC tracks just three state variables, which it updates
each time it receives a new acknowledgment:

@@

\item An exponentially-weighted moving average (EWMA) of the
  interarrival time between new acknowledgments received ({\tt
    ack\_ewma}).

\item An exponentially-weighted moving average of the time between TCP
  sender timestamps reflected in those acknowledgments ({\tt
    send\_ewma}). A weight of $1/8$ is given to the new sample in both
  EWMAs.

@@

Together, we call these three variables the {\em RemyCC memory}. It is
worth reflecting on these variables, which are the
``congestion signals'' used by any RemyCC. We narrowed the memory to
this set after examining and discarding quantities like the
most-recent RTT sample, the smoothed RTT estimate, and the difference
between the long-term EWMA and short-term EWMA of the observed packet
rate or RTT. In our experiments, adding extra state variables didn't improve
the performance of the resulting protocol, and each additional
dimension slows down the design procedure considerably. But we don't
claim that Remy's three state variables are the only set that works,
or that they are necessarily optimal for all situations a protocol
might encounter. We expect that any group of estimates that roughly
summarizes the recent history could form the basis of a workable
congestion-control scheme.

@@

A RemyCC is defined by a set of piecewise-constant \emph{rules}, each one
mapping a three-dimensional rectangular region of the
three-dimensional memory space to a three-dimensional action:
$$
\langle {\tt ack\_ewma}, {\tt send\_ewma}, {\tt rtt\_ratio} \rangle \rightarrow
\langle m, b, r \rangle.
$$

@@

The design phase of Remy is an optimization procedure to efficiently
construct this state-to-action mapping, or \emph{rule table}.  Remy uses simulation of the senders on
various sample networks drawn from the network model, with
parameters drawn within the ranges of the supplied prior
assumptions. These parameters include the link rates, delays, the
number of sources, and the on-off distributions of the
sources. Offline, Remy
evaluates candidate algorithms on
millions of randomly generated network configurations. Because of the
high speed of current computers and the ``embarrassingly parallel''
nature of the task, Remy is able to generate congestion-control
algorithms within a few hours.

@@

A single evaluation step, the innermost loop of Remy's design process,
consists of drawing 16 or more network specimens from the network
model, then simulating the RemyCC algorithm at each sender for 100
seconds on each network specimen. At the end of the simulation, the
objective function for each sender, given by Equation~\ref{eq:util},
is totaled to produce an overall figure of merit for the RemyCC. We
explore two cases, $\alpha = \beta = 1$ and $\alpha=2, \delta =
0$. The first case corresponds to proportional throughput and delay
fairness, maximizing $$U = \log (\mbox{throughput}) - \delta \cdot
\log (\mbox{delay}),$$ with $\delta$ specifying the importance placed
on delay vs.~throughput. The second case corresponds to minimizing the
potential delay of a fixed-length transfer, by maximizing $$U =
-\frac{1}{\mbox{throughput}}.$$

@@

Remy initializes a RemyCC with only a single rule. Any values of the
three state variables (between 0 and 16,384) are mapped to a default
action where $m = 1$, $b = 1$, $r = 0.01$.

@@

\item \textbf{Subdivide the most-used rule.} Recall that each rule
  represents a mapping from a three-dimensional rectangular region of
  memory space to a single action. In this step, find the most-used
  rule, and the median memory value that triggers it. Split the rule
  at this point, producing eight new rules (one per dimension of the
  memory-space), each with the same action as before. Then return to
  step 1.

@@

By repeating this procedure, the structure of a RemyCC's rule table
becomes an
octree~\cite{octree}
of memory regions. Areas of the memory space more likely to occur
receive correspondingly more attention from the optimizer, and are
subdivided into smaller bins that yield a more granular function
relating memory to action. \emph{Which} rules are more often triggered
depends on every endpoint's behavior as well as the network's
parameters, so the task of finding the right structure for the rule
table is best run alongside the process of optimizing existing rules.

To the best of our knowledge, this dynamic partitioning approach is
novel in the context of multi-agent optimization. The ``greedy''
approach in step 2 is key to the computational tractability and
efficiency of the search because it allows us to prune the search
space. Dividing the memory space into cells of different size
proportional to their activity produces a rule table
whose granularity is finer in regions of higher use. An improvement to
consider in the future is to divide a cell only if the actions at its
boundaries markedly disagree.\footnote{We thank Leslie Kaelbling for
  this suggestion.}

>>>>

Instead, we approximate the solution by greatly abridging the sender's
state. A RemyCC tracks three or four features of the history, which it
updates each time it receives a new acknowledgment:

@@

\item An exponentially-weighted moving average (EWMA) of the
  interarrival time between new acknowledgments received ({\tt
    ack\_ewma}), where each new sample contributes 1/8 of the weight
  of the moving average.

\item In some RemyCCs, where the goal is operation over a broad range
  of networks, we consider the same feature but with a longer-term
  moving average, using a weight of 1/256 for the newest sample.

\item An exponentially-weighted moving average of the time between TCP
  sender timestamps reflected in those acknowledgments ({\tt
    send\_ewma}), again with a weight of 1/8 to each new sample.

@@

Together, we call these variables the {\em RemyCC memory}. It is worth
reflecting on these variables, which are the ``congestion signals''
used by any RemyCC. The value of these signals can be measured
empirically, by ``knocking out'' a signal and examining the resulting
effect on performance. We narrowed the memory to this set after
examining and discarding quantities like the most-recent RTT sample,
the smoothed RTT estimate, and the difference between the long-term
EWMA and short-term EWMA of the observed packet rate or RTT. In our
experiments, adding extra state variables didn't improve the
performance of the resulting protocol, and each additional dimension
slows down the design procedure considerably. But we cannot claim that
Remy's state variables are necessarily optimal for all situations a
protocol might encounter. We expect that any group of estimates that
roughly summarizes the recent history could form the basis of a
workable congestion-control scheme.

@@

A RemyCC is defined by a set of piecewise-constant \emph{rules}, each
one mapping a rectangular region of the three- or four-dimensional
memory space to a three-dimensional action:
$$
\langle {\tt ack\_ewma}, {\tt send\_ewma}, {\tt rtt\_ratio} \rangle \rightarrow
\langle m, b, r \rangle.
$$

@@

The design phase of Remy is an optimization procedure to efficiently
construct this state-to-action mapping, or \emph{rule table}.  Remy uses simulation of the senders on
various sample networks drawn from the network model, with
parameters drawn within the ranges of the supplied prior
assumptions. These parameters include the link rates, delays, the
number of sources, and the on-off distributions of the
sources. Offline, Remy
evaluates candidate algorithms on
millions of randomly generated network configurations.

@@

A single evaluation step consists of drawing somewhere between 16 and
100 network specimens from the network model, then simulating the
RemyCC algorithm at each sender an extended length of time on each
network specimen. At the end of the simulation, the objective function
for each sender, given by Equation~\ref{eq:util}, is totaled to
produce an overall figure of merit for the RemyCC. We explore two
cases, $\alpha = \beta = 1$ and $\alpha=2, \delta = 0$. The first case
corresponds to proportional throughput and delay fairness,
maximizing $$U = \log (\mbox{throughput}) - \delta \cdot \log
(\mbox{delay}),$$ with $\delta$ specifying the importance placed on
delay vs.~throughput. The second case corresponds to minimizing the
potential delay of a fixed-length transfer, by maximizing $$U =
-\frac{1}{\mbox{throughput}}.$$

@@

Remy initializes a RemyCC with only a single rule. Any values of the
state variables (between 0 and 16,384) are mapped to a default action
where $m = 1$, $b = 1$, $r = 0.01$.

@@

\item \textbf{Subdivide the most-used rule.} Recall that each rule
  represents a mapping from a rectangular region of memory space to a
  single action. In this step, find the most-used rule, and the median
  memory value that triggers it. Split the rule at this point,
  producing eight new rules (one per dimension of the memory-space),
  each with the same action as before. Then return to step 1.

@@

By repeating this procedure, the structure of a RemyCC's rule table
becomes an octree~\cite{octree} or hextree of memory regions. Areas of
the memory space more likely to occur receive correspondingly more
attention from the optimizer, and are subdivided into smaller bins
that yield a more granular function relating memory to
action. \emph{Which} rules are more often triggered depends on every
endpoint's behavior as well as the network's parameters, so the task
of finding the right structure for the rule table is best run
alongside the process of optimizing existing rules.

To the best of our knowledge, this dynamic partitioning approach is
novel in the context of multi-agent optimization. The ``greedy''
approach in step 2 is key to the computational tractability and
efficiency of the search because it allows us to prune the search
space. Dividing the memory space into cells of different size
proportional to their activity produces a rule table
whose granularity is finer in regions of higher use.

### 2014-05-08 remy_eval.tex
Edit thru chapter 3

In addition, we investigate:
\begin{enumerate} 
\item[5.] {\bf Competing protocols:} We assessed how a RemyCC ``played with''
  existing congestion-control schemes (Cubic and Compound) when contending
  for the same bottleneck link.
\item [6.] {\bf Sensitivity of design range:} We investigated how
  helpful prior knowledge of the network is to the performance of
  Remy's generated algorithms.
\end{enumerate}

@@

\includegraphics[width=\columnwidth]{rttfairness.pdf}
\caption{Remy's RTT unfairness compares favorably to
  Cubic-over-sfqCoDel. Error bar represents standard error of the
  mean over 128 100-second simulations.}

@@

\subsection{Competing protocols}

@@

>>>>

%In addition, we investigate:
%\begin{enumerate} 
%\item[5.] {\bf Competing protocols:} We assessed how a RemyCC ``played with''
%  existing congestion-control schemes (Cubic and Compound) when contending
%  for the same bottleneck link.
%\item [6.] {\bf Sensitivity of design range:} We investigated how
%  helpful prior knowledge of the network is to the performance of
%  Remy's generated algorithms.
%\end{enumerate}

@@

\includegraphics[width=\columnwidth]{rttfairness.pdf}
\caption{The RemyCCs' RTT unfairness compares favorably to
  Cubic-over-sfqCoDel. Error bar represents standard error of the mean
  over 128 100-second simulations.}

@@

\begin{comment}
\subsection{Competing protocols}

@@

\end{comment}

### 2014-05-08 remy_intro.tex
Add some results to sprout section of intro
Edit thru chapter 3

\section{Introduction}
\label{remy:intro}

Is it possible for a computer to ``discover'' the right rules for
congestion control in heterogeneous and dynamic networks? Should
computers, rather than humans, be tasked with developing congestion
control methods?  And just how well can we make computers perform this
task?

We investigated these questions and found that computers can design
schemes that in some cases surpass the best human-designed methods to
date, when supplied with the appropriate criteria by which to
judge a congestion-control algorithm. We attempt to probe the limits
of these machine-generated protocols, and discuss how this style of
transport-layer protocol design can give more freedom to network
architects and link-layer designers.

@@

Congestion control, a fundamental problem in multi-user computer
networks, addresses the question: when should an endpoint transmit
each packet of data? An ideal scheme would transmit a packet whenever
capacity to carry the packet was available, but because there are many
concurrent senders and the network experiences variable delays, this
question isn't an easy one to answer. On the Internet, the past thirty
years have seen a number of innovative and influential answers to this
question, with solutions embedded at the endpoints (mainly in TCP)
aided occasionally by queue management and scheduling algorithms in
bottleneck routers that provide signals to the endpoints.

@@

Without the ability to adapt its congestion-control algorithms to new
scenarios, TCP's inflexibility constrains architectural evolution, as
we noted in an earlier position paper~\cite{hotnets2011}. Subnetworks
and link layers are typically evaluated based on how well TCP performs
over them.  This scorecard can lead to perverse behavior, because
TCP's network model is limited. For example, because TCP assumes that
packet losses are due to congestion and reduces its transmission rate
in response, some subnetwork designers have worked hard to hide
losses. This often simply adds intolerably long packet delays. One may
argue that such designs are misguided, but the difficulties presented
by ``too-reliable'' link layers have been a perennial challenge for 25
years~\cite{Clark88} and show no signs of abating. With the rise of
widespread cellular connectivity, these behaviors are increasingly
common and deeply embedded in deployed infrastructure.

@@

\subsection*{Design overview}

How should we design network protocols that free subnetworks and links
to evolve freely, ensuring that the endpoints will adapt properly
\emph{no matter what} the lower layers do?  We believe that the best
way to approach this question is to take the design of specific
algorithmic mechanisms out of the hands of human designers (no matter
how sophisticated!), and make the end-to-end algorithm be a function
of the desired overall behavior.

@@

We have developed an optimization tool called Remy that takes these
models as input, and designs a congestion-control algorithm that tries
to maximize the total expected value of the objective function, measured over the set of
network and traffic models. The resulting pre-calculated, optimized
algorithm is then run on actual endpoints; no further learning happens
after the offline optimization. The optimized algorithm is run as part
of an existing TCP sender implementation, or within any
congestion-control module. No receiver changes are necessary (as of
now).

\subsection*{Summary of results}

We have implemented Remy. Running on a 48-core server at MIT, Remy
generally takes a few hours of wall-clock time (one or two CPU-weeks)
to generate congestion-control algorithms offline that work on a wide
range of network conditions.

@@

\item Comparing Remy's algorithms with schemes that require
  modifications to network gateways, including Cubic-over-sfqCoDel and
  XCP, Remy generally matched or surpassed these schemes, despite
  being entirely end-to-end.

\item We measured the tradeoffs that come from specificity in the
  assumptions supplied to Remy at design time. As expected,
  more-specific prior information turned out to be helpful when it was
  correct, but harmful when wrong. We found that RemyCC schemes
  performed well even when designed for an order-of-magnitude
  variation in the values of the underlying network parameters.
\end{enumerate}

@@

{\footnotesize
\begin{tabular}{|l|c|c|}
\hline
Protocol & Median speedup & Median delay reduction \\
\hline
\hline
Compound & $2.1\times$ & $2.7\times$ \\
NewReno & $2.6\times$ & $2.2\times$ \\
Cubic & $1.7\times$ & $3.4\times$ \\
Vegas & $3.1\times$ & $1.2\times$ \\
\hline
Cubic/sfqCoDel & $1.4\times$ & $7.8\times$ \\
XCP & $1.4\times$ & $4.3\times$ \\
\hline
\end{tabular}
}

@@

{\footnotesize
\begin{tabular}{|l|c|c|}
\hline
Protocol & Median speedup & Median delay reduction \\
\hline
\hline
Compound & $1.3\times$ & $1.3\times$ \\
NewReno & $1.5\times$ & $1.2\times$ \\
Cubic & $1.2\times$ & $1.7\times$ \\
Vegas & $2.2\times$ & $0.44\times \downarrow$ \\
\hline
Cubic/sfqCoDel & $1.3\times$ & $1.3\times$ \\
XCP & $1.7\times$ & $0.78\times \downarrow$ \\
\hline
\end{tabular}
}

The source code for Remy, our ns-2 models, and the algorithms that Remy
designed are available from \mbox{\url{http://web.mit.edu/remy}}.

>>>>

%\section{Introduction}
\label{remy:intro}

Sprout (Chapter~\ref{chap:sprout}) addressed a particular problem in
congestion control: the compromise between throughput and delay on a
cellular network, where the user has his or her own queue at the
bottleneck but does not know the capacity of the link.

The classical problem of distributed resource allocation on the
Internet, however, is more challenging than this. Algorithms like TCP
NewReno~\cite{newreno} and Cubic~\cite{cubic} are designed for the
problem of \emph{multi-agent} congestion control. In general, multiple
independent users may contend for the same bottleneck---without
knowing for certain how many other users they are contending with.

Is it possible, then, for a computer to design an algorithm from first
principles and ``discover'' the right rules for congestion control? We
found that computers can design schemes that in some cases surpass the
best human-designed methods to date, when supplied with the
appropriate criteria by which to judge a congestion-control
algorithm. We attempt to probe the limits of these machine-generated
protocols, and discuss how this style of transport-layer protocol
design can give more freedom to network architects and link-layer
designers.

@@

Congestion control is a fundamental problem in multi-user computer
networks. Any proposed solution must answer the question: when should
an endpoint transmit each packet of data? An ideal scheme would
transmit a packet whenever capacity to carry the packet was available,
but because there are many concurrent senders and the network
experiences variable delays, this question isn't an easy one to
answer. On the Internet, the past thirty years have seen a number of
innovative and influential answers to this question, with solutions
embedded at the endpoints (mainly in TCP) aided occasionally by queue
management and scheduling algorithms in bottleneck routers that
provide signals to the endpoints.

@@

Without the ability to adapt its congestion-control algorithms to new
scenarios, TCP's inflexibility constrains architectural
evolution~\cite{hotnets2011}. Subnetworks and link layers are
typically evaluated based on how well TCP performs over them.  This
scorecard can lead to perverse behavior, because TCP's network model
is limited. For example, because TCP assumes that packet losses are
due to congestion and reduces its transmission rate in response, some
subnetwork designers have worked hard to hide losses. This often
simply adds intolerably long packet delays. One may argue that such
designs are misguided, but the difficulties presented by
``too-reliable'' link layers have been a perennial challenge for 25
years~\cite{Clark88} and show no signs of abating. With the rise of
widespread cellular connectivity, these behaviors are increasingly
common and deeply embedded in deployed infrastructure.

@@

\section{Design overview}

%How should we design network protocols that free subnetworks and links
%to evolve freely, ensuring that the endpoints will adapt properly
%\emph{no matter what} the lower layers do?  We believe that the best
%way to approach this question is to take the design of specific
%algorithmic mechanisms out of the hands of human designers (no matter
%how sophisticated!), and make the end-to-end algorithm be a function
%of the desired overall behavior.

@@

I developed an optimization tool called Remy that takes these models
as input, and designs a congestion-control algorithm that tries to
maximize the total expected value of the objective function, measured
over the set of network and traffic models. The resulting
pre-calculated, optimized algorithm is then run on actual endpoints;
no further learning happens after the offline optimization. The
optimized algorithm is run as part of an existing TCP sender
implementation, or within any congestion-control module. No receiver
changes are necessary (as of now).

\section{Summary of results}

I implemented Remy in C++. Running on an 80-core server at MIT, Remy
generally takes between a few hours to a few days of wall-clock time
(up to a CPU-year) to generate congestion-control algorithms offline
that work on a wide range of network conditions.

@@

\item Comparing Remy's algorithms with schemes that require
  modifications to network gateways, including Cubic-over-sfqCoDel and
  XCP, Remy generally matched or surpassed these schemes, despite
  being entirely end-to-end.
\end{enumerate}

@@

\label{sec:remyresults}

\begin{center}

\begin{tabular}{|l|c|c|}
\hline
Protocol & Median speedup & Median delay reduction \\
\hline
\hline
Compound & $2.1\times$ & $2.7\times$ \\
NewReno & $2.6\times$ & $2.2\times$ \\
Cubic & $1.7\times$ & $3.4\times$ \\
Vegas & $3.1\times$ & $1.2\times$ \\
\hline
Cubic/sfqCoDel & $1.4\times$ & $7.8\times$ \\
XCP & $1.4\times$ & $4.3\times$ \\
\hline
\end{tabular}

\end{center}

@@

\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Protocol & Median speedup & Median delay reduction \\
\hline
\hline
Compound & $1.3\times$ & $1.3\times$ \\
NewReno & $1.5\times$ & $1.2\times$ \\
Cubic & $1.2\times$ & $1.7\times$ \\
Vegas & $2.2\times$ & \cellcolor{red!20}$0.44\times$ \\
\hline
Cubic/sfqCoDel & $1.3\times$ & $1.3\times$ \\
XCP & $1.7\times$ & \cellcolor{red!20}$0.78\times$ \\
\hline
\end{tabular}

\end{center}

The source code for Remy, our ns-2 models, the algorithms that Remy
designed, and instructions for replicating the experiments and
reproducing the figures in this chapter are available from
\mbox{\url{http://mit.edu/remy}}.

### 2014-05-08 remy_limits.tex
Edit thru chapter 3

\section{Discussion}

Much remains unknown about the capabilities and limits of
computer-generated algorithms, much less decentralized algorithms that
cooperate indirectly across a network to achieve a common
goal. Although the RemyCCs appear to work well on networks whose
parameters fall within or near the limits of what they were prepared
for --- even beating in-network schemes at their own game and even
when the design range spans an order of magnitude variation in network
parameters --- we do not yet understand clearly \emph{why} they work,
other than the observation that they seem to optimize their intended
objective well.

We have attempted to make algorithms ourselves that surpass the
generated RemyCCs, without success. That suggests to us that Remy may
have accomplished something substantive. But digging through the
dozens of rules in a RemyCC and figuring out their purpose and
function is a challenging job in reverse-engineering. RemyCCs
designed for broader classes of networks will likely be even
more complex, compounding the problem.

Our approach \emph{increases} endpoint complexity in order to
\emph{reduce} the complexity of overall network behavior. Traditional
TCP congestion control specifies simpler behavior for each endpoint,
but the resulting emergent behavior of a multiuser network is not
easily specified and is often suboptimal and variable, and even
unstable.

By contrast, our approach focuses on maximizing a well-specified
overall objective at the cost of complex endpoint algorithms. We think
this tradeoff is advisable: today's endpoints can execute complex
algorithms almost as easily as simple ones (and with Remy, the bulk of
the intelligence is computed offline). What users and system designers
ultimately care about, we believe, is the quality and consistency of
overall behavior.

Our {\em synthesis-by-simulation} approach also makes it easier to
\emph{discuss} competing proposals for congestion control. Today, it
is not easy to say why one flavor of TCP or tweak may be preferred
over another. But if two computer-generated algorithms differ, there is
a reason: either they make different assumptions about the expected
networks they will encounter, or they have different goals in mind, or
one is better optimized than the other. This formulation allows the
implementer to choose rationally among competing options.

All that said, we have much to learn before computer-generated
algorithms will have proven themselves trustworthy:

\begin{itemize}

\item Other than by exhaustive testing, we don't know how to predict
  the robustness of RemyCCs to unexpected inputs. Do they break
  catastrophically in such situations?

\item How would a RemyCC designed for a 10,000-fold range of
  throughputs and RTTs perform?
%, compared with existing algorithms?
%We do not know how a RemyCC's performance will be affected as
%  its prior knowledge becomes less specific and the optimization
%  procedure more arduous.

\item Although we are somewhat robust against a RemyCC's latching on
  to the peculiarities of a simulator implementation (because RemyCCs
  are designed within Remy but then evaluated within ns-2), we can't
  be certain how well RemyCCs will perform on real networks without
  trying them.

% We have not exhaustively cataloged the behavior of
%even the RemyCCs discussed in this paper.
%, and we have not yet tried to
%design a congestion-control protocol that resists being ``squeezed
%out'' by heterogenous incumbent protocols.

\end{itemize}

We believe that making congestion control a \emph{function} of the
desired ends, and the assumptions we make about the network, is the
solution to allow the Internet and its subnetworks to evolve without
tiptoeing around TCP's assumptions about how networks behave. But many
dots need to be connected before the the Internet at large --- as
opposed to internal networks --- might agree on a model that could be
used to prepare a ``one-size-fits-all'' RemyCC.

>>>>

\section{Ratatouille, a tool for understanding RemyCCs}

The use of computer-generated congestion-control algorithms presents
different engineering challenges than conventional designs. In
practice, RemyCCs \emph{increase} endpoint complexity in order to
\emph{reduce} the complexity of overall network behavior.

Traditional TCP congestion control specifies simpler behavior for each
endpoint, but the resulting emergent behavior of a multiuser network
is not easily specified and is often suboptimal and variable, and even
unstable. By contrast, our approach focuses on maximizing a
well-specified overall objective at the cost of complex endpoint
algorithms.

We think this tradeoff is ultimately worth taking: today's endpoints
can execute complex algorithms almost as easily as simple ones (and
with Remy, the bulk of the intelligence is computed offline). What
users and system designers ultimately care about, we believe, is the
quality and consistency of overall behavior.

But when endpoint algorithms become very complex, figuring out
\emph{why} a particular RemyCC works involves a reverse-engineering
challenge. To help with this task, I built a visualization and
debugging tool for RemyCCs, called Ratatouille.

Ratatouille displays real-time output from the Remy network simulator,
and plots the current number of packets-in-flight for each concurrent
flow as it evolves over time. The user interacts with a physical USB
control surface---originally intended to control a software music
mixing application---to vary the network parameters: the number of
flows with offered load, the link rate, propagation delay, and buffer
size at the bottleneck queue. The user can then observe how the flows
respond to the changing conditions. (For comparison, Ratatouille can
also run a conventional AIMD TCP-like algorithm.)

By exploring the evolving values of the congestion signals at each
sender as the network changes, we have gained some intuition into how
a RemyCC can achieve good throughput and low delay. When the network
is in steady state, the congestion signals of a RemyCC sender tend to
fall into an orbit, or limit cycle, in which the average number of
packets in flight over the cycle is close to the ``ideal'' number: the
bandwidth-delay product of the bottleneck link divided by the degree
of multiplexing.

The period of the limit cycles is generally a small number of
minRTTs. By contrast, TCP's congestion window typically oscillates on
a much longer timescale that depends on the buffer size, because the
``multiplicative decrease'' feature of TCP's control rules is only
triggered when packet loss is detected (in other words, only after
buffer overflow occurs in the bottleneck queue).

This suggests that a RemyCC's ability to achieve better throughput
than TCP on finite-length flows is mostly due to its quicker response
to changes in conditions---a RemyCC will generally ``ramp up'' to the
ideal number of packets-in-flight more quickly than the TCP
slow-start algorithm.

Although Ratatouille has allowed us to make observations that suggest
``why'' RemyCCs achieve their good performance compared with
human-designed mechanisms, much more work will be necessary before we
can reason about the performance and robustness of RemyCCs in a
rigorous way.

\begin{figure}
\caption{Ratatouille allows a user to vary network conditions on a
  physical control service, then observe the resulting behavior of a
  RemyCC in real-time.}
\label{fig:ratscreen}

\begin{center}

(XXX insert screenshot)

\end{center}
\end{figure}

### 2014-05-08 remy_model.tex
Edit thru chapter 3

Our approach hinges on being able to evaluate quantitatively the merit
of any particular congestion control algorithm, and search for the
best algorithm for a given network model and objective function. We
discuss here our models of the network and cross traffic, and how we
ultimately calculate a figure of merit for an arbitrary congestion
control algorithm.

@@

Currently, we typically parametrize networks on three axes: the speed
of bottleneck links, the propagation delay of the network paths, and
the degree of multiplexing, i.e., the number of senders contending for
each bottleneck link. We assume that senders have no control over the
paths taken by their packets to the receiver.

@@

As one might expect, we have observed a tradeoff between generality
and performance; a protocol designed for a broad range of networks may
be beaten by a protocol that has been supplied with more specific and
accurate prior knowledge. Our approach allows protocol designers to
measure this tradeoff and choose an appropriate design range for their
applications.

@@

We emphasize that the purpose of the objective function is to supply a
quantitative goal from a protocol-design perspective. It need not
(indeed, does not) precisely represent users' ``true'' preferences or
utilities. In real usage, different users may have different
objectives; a videoconference may not benefit from more throughput, or
some packets may be more important than others. We have not yet
addressed the problem of how to accommodate diverse objectives or how
endpoints might learn about the differing preferences of other
endpoints.

>>>>

The Remy approach hinges on being able to evaluate quantitatively the
merit of any particular congestion control algorithm, and search for
the best algorithm for a given network model and objective function. I
describe here our models of the network and cross traffic, and how we
ultimately calculate a figure of merit for an arbitrary congestion
control algorithm.

@@

We have typically parametrized networks on three axes: the speed of
bottleneck links, the propagation delay of the network paths, and the
degree of multiplexing, i.e., the number of senders contending for
each bottleneck link. We assume that senders have no control over the
paths taken by their packets to the receiver.

@@

We have observed only weak evidence for a tradeoff between generality
and performance; a protocol designed for a broad range of networks may
be beaten by a protocol that has been supplied with more specific and
accurate prior knowledge. Quantifying and characterizing these kind of
tradeoffs is the subject of Chapter~\ref{chap:learnability}.

@@

We emphasize that the purpose of the objective function is to supply a
quantitative goal from a protocol-design perspective. It need not
(indeed, does not) precisely represent users' ``true'' preferences or
utilities. In real usage, different users may have different
objectives; a videoconference may not benefit from more throughput, or
some packets may be more important than others. In
Chapter~\ref{chap:learnability}, we discuss the problem of how to
accommodate diverse objectives on the same network.

### 2014-05-08 remy_related.tex
Edit thru chapter 3

In this paper, we compare Remy's generated algorithms with several
end-to-end schemes, including NewReno~\cite{newreno},
Vegas~\cite{vegas}, Compound TCP~\cite{compound}, Cubic~\cite{cubic},
and DCTCP for datacenters~\cite{dctcp}. NewReno has the same
congestion-control strategy as Reno---slow start at the beginning, on
a timeout, or after an idle period of about one retransmission timeout
(RTO), additive increase every RTT when there is no congestion, and a
one-half reduction in the window on receiving three duplicate ACKs
(signaling packet loss). We compare against NewReno rather than Reno
because NewReno's loss recovery is better.

@@

We note that TCP stacks have adapted in some respects to the changing
Internet; for example, increasing bandwidth-delay products have
produced efforts to increase the initial congestion
window~\cite{dukkipati2010argument,chu2012increasing}, including
recent proposals \cite{allman2010init,touch2012automating} for this
quantity to automatically increase on the timescale of months or
years. What we propose in this paper is an automated means by which
TCP's entire congestion-control algorithm, not just its initial
window, could adapt in response to empirical variations in underlying
networks.

>>>>

In evaluating Remy, we compare its output---the computer-generated
algorithms---with several end-to-end schemes, including
NewReno~\cite{newreno}, Vegas~\cite{vegas}, Compound
TCP~\cite{compound}, Cubic~\cite{cubic}, and DCTCP for
datacenters~\cite{dctcp}. NewReno has the same congestion-control
strategy as Reno---slow start at the beginning, on a timeout, or after
an idle period of about one retransmission timeout (RTO), additive
increase every RTT when there is no congestion, and a one-half
reduction in the window on receiving three duplicate ACKs (signaling
packet loss). We compare against NewReno rather than Reno because
NewReno's loss recovery is better.

@@

We note that TCP stacks have adapted in some respects to the changing
Internet; for example, increasing bandwidth-delay products have
produced efforts to increase the initial congestion
window~\cite{dukkipati2010argument,chu2012increasing}, including
recent proposals \cite{allman2010init,touch2012automating} for this
quantity to automatically increase on the timescale of months or
years. Remy represents an automated means by which TCP's entire
congestion-control algorithm, not just its initial window, could adapt
in response to empirical variations in underlying networks.
